Template for indicator documentation

### 2023-09-12 DRAFT_insectIndicators.Rmd
Update DRAFT_insectIndicators.Rmd
correction of some more typos

### Data sets
There are a few different ways to access the data required for these indicators. Both the NMBB and the NorIns project stores its data in an internal database at NINA. They both also export most of their data to GBIF, but those exports need to be restructured before they can be processed in the following scripts.

@@

The indicators from the NMBB program is similary connected to regions, with the exception that the south-east region only covers the old fylke's of Vestfold and Østfold, and that Nord-Norge isn't covered yet.

@@

Compare values to a reference state. The reference state is here set uniformly for all regions, with a made up value just to be able to continue the calculations. Alternatively, we could calculate the indicator values for each region separately, compare to individual reference states, and then put it all together again.

@@

Divide the richness of parasitica by symphyta. [Could make a function for this later on.]

@@

Bootstrap the fraction of parasitica to symphyta.

@@

The calculations for earlier years is already present as datasets in the R-package and can be fetched individually. Once this is done, we can plot the timeseries of values using the function `indPlot`.

>>>>

### Data sets
There are a few different ways to access the data required for these indicators. Both the NMBB and the NorIns project store their data in an internal database at NINA. They both also export most of their data to GBIF, but those exports need to be restructured before they can be processed in the following scripts.

@@

The indicators from the NMBB program are similary connected to regions, with the exception that the south-east region only covers the old counties of Vestfold and Østfold, and that Nord-Norge isn't covered yet.

@@

Compare values to a reference state. The reference state is here set uniformly for all regions, with a made-up value just to be able to continue the calculations. Alternatively, we could calculate the indicator values for each region separately, compare to individual reference states, and then put it all together again.

@@

Divide the richness of Parasitica by Symphyta. [Could make a function for this later on.]

@@

Bootstrap the fraction of Parasitica to Symphyta.

@@

The calculations for earlier years are already present as datasets in the R-package and can be fetched individually. Once this is done, we can plot the timeseries of values using the function `indPlot`.
